\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-10 doc/paper.tex
moving the SLHA input file to the appendix

\section{Run-time comparison with other spectrum generators}
\label{Sec:comparison}
We compare the run-time of five different CMSSM spectrum generators:
\begin{itemize}
\item FlexibleSUSY-FV (version 1.0.0), which is based on SARAH's MSSM
  model file that allows flavour violation,
\item FlexibleSUSY-NoFV (version 1.0.0), without flavour violation
\item Softsusy (version 3.4.0), without flavour violation
\item SPheno (3.2.4), without flavour violation
\item SPhenoMSSM (generated with SARAH 4.1.0 and linked against SPheno
  3.2.4), which uses SARAH's MSSM model file that includes flavour
  violation.
\end{itemize}
FlexibleSUSY and Softsusy were compiled with g++ 4.8.0 and Intel ifort
13.1.3 20130607.  SPheno and SPhenoMSSM were compiled with Intel ifort
13.1.3 20130607\footnote{We are using Intel's ifort compiler, instead
  of gfortran, because it decreases the run-time of SPheno and
  SPhenoMSSM by approximately a factor $1.5$.}.  We're generating
$2\cot 10^{4}$ random CMSSM parameter points with $m_0\in [50,1000]$
$m_{1/2}\in [50,1000]$, $\tan\beta\in [1,100]$, $\sign\mu\in
\{-1,+1\}$ and $A_0\in [-1000,1000]$.  The following SLHA template
file was used:
\begin{verbatim}
Block MODSEL                 # Select model
    6    0                   # flavour violation
    1    1                   # mSUGRA
Block SMINPUTS               # Standard Model inputs
    1   1.279180000e+02      # alpha^(-1) SM MSbar(MZ)
    2   1.166390000e-05      # G_Fermi
    3   1.189000000e-01      # alpha_s(MZ) SM MSbar
    4   9.118760000e+01      # MZ(pole)
    5   4.200000000e+00      # mb(mb) SM MSbar
    6   1.709000000e+02      # mtop(pole)
    7   1.777000000e+00      # mtau(pole)
Block SOFTSUSY               # SOFTSUSY specific inputs
    1   1.000000000e-04      # tolerance
    2   2                    # up-quark mixing (=1) or down (=2)
    3   0                    # printout
    5   1                    # 2-loop running
    7   2                    # EWSB and Higgs mass loop order
Block FlexibleSUSY
    0   1.000000000e-04      # precision goal
    1   0                    # max. iterations (0 = automatic)
    2   0                    # algorithm (0 = two_scale, 1 = lattice)
    3   0                    # calculate SM pole masses
    4   1                    # pole mass loop order
    5   1                    # EWSB loop order
Block SPhenoInput            # SPheno specific input
    1  -1                    # error level
    2   1                    # SPA conventions
    11  0                    # calculate branching ratios
    13  0                    # include 3-Body decays
    12  1.000E-04            # write only branching ratios larger than this value
    31  -1                   # fixed GUT scale (-1: dynamical GUT scale)
    32  0                    # Strict unification
    34  1.000E-04            # Precision of mass calculation
    35  40                   # Maximal number of iterations
    37  1                    # Set Yukawa scheme
    38  2                    # 1- or 2-Loop RGEs
    50  1                    # Majorana phases: use only positive masses
    51  0                    # Write Output in CKM basis
    52  0                    # Write spectrum in case of tachyonic states
    55  1                    # Calculate one loop masses
    57  0                    # Calculate low energy constraints
    60  0                    # Include possible, kinetic mixing
    65  1                    # Solution tadpole equation
    75  0                    # Write WHIZARD files
    76  0                    # Write HiggsBounds file
    86  0.                   # Maximal width to be counted as invisible in Higgs decays
    510 0.                   # Write tree level values for tadpole solutions
    515 0                    # Write parameter values at GUT scale
    520 0.                   # Write effective Higgs couplings (HiggsBounds blocks)
    525 0.                   # Write loop contributions to diphoton decay of Higgs
Block MINPAR
    1   [50..1000]           # m0(MX)
    2   [50..1000]           # m12(MX)
    3   [1..100]             # tan(beta)(MZ) DRbar
    4   {-1,+1}              # sign(mu)
    5   [-1000..1000]        # A0(MX)
\end{verbatim}
The SLHA file was passed to each spectrum generator and the
(wall-clock) time was measured until the program has finished.  The
average run-times for three different CPU types can be found in
\tablename~\ref{tab:run-time-comparison}.  The first column shows the
run-time on a Intel Core2 Duo (P8600) where only one core was enabled.
The second column shows the run-time on a Intel Core2 Duo (P8600)
where both cores were enabled.  In the third column a Intel Xeon
(L5640) was used, which has $6$ CPU cores.
\begin{table}[tbh]
  \begin{tabular}{llll}
    \toprule
                          & Intel Core2 Duo (P8600)    & Intel Core2 Duo (P8600)     & Intel Xeon (L5640)\\
                          & (1 core, $2.40\unit{GHz}$) & (2 cores, $2.40\unit{GHz}$) & (6 cores, $2.27\unit{GHz}$)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$  & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators for
    for random parameter points.  The upper }
  \label{tab:run-time-comparison}
\end{table}

@@

>>>>

\section{Run-time comparison with other spectrum generators}
\label{Sec:comparison}
We compare the run-time of five different CMSSM spectrum generators:
%
\begin{itemize}
\item FlexibleSUSY-FV (version 1.0.0), which is based on SARAH's MSSM
  model file that allows flavour violation,
\item FlexibleSUSY-NoFV (version 1.0.0), without flavour violation
\item Softsusy (version 3.4.0), without flavour violation
\item SPheno (3.2.4), without flavour violation
\item SPhenoMSSM (generated with SARAH 4.1.0 and linked against SPheno
  3.2.4), which uses SARAH's MSSM model file that includes flavour
  violation.
\end{itemize}
%
FlexibleSUSY and Softsusy are compiled with g++ 4.8.0 and Intel ifort
13.1.3 20130607.  SPheno and SPhenoMSSM are compiled with Intel ifort
13.1.3 20130607\footnote{We are using Intel's ifort compiler, instead
  of gfortran, because it decreases the run-time of SPheno and
  SPhenoMSSM by approximately a factor $1.5$.}.  We're generating
$2\cdot 10^{4}$ random CMSSM parameter points with $m_0\in [50,1000]$
$m_{1/2}\in [50,1000]$, $\tan\beta\in [1,100]$, $\sign\mu\in
\{-1,+1\}$ and $A_0\in [-1000,1000]$.  For each point an SLHA input
file is created by appending the values of $m_0$, $m_{1/2}$,
$\tan\beta$, $\sign\mu$, $A_0$ in form of a \code{MINPAR} block to the
SLHA template file given in \ref{sec:speed-test-slha-template-file}.
The resulting SLHA input file is passed to each spectrum generator and
the (wall-clock) time is measured until the program has finished.  The
average run-times for three different CPU types can be found in
\tablename~\ref{tab:run-time-comparison}.  The first column shows the
run-time on a Intel Core2 Duo (P8600) where only one core was enabled.
The second column shows the run-time on a Intel Core2 Duo (P8600)
where both cores were enabled.  In the third column a Intel Xeon
(L5640) was used, which has $6$ CPU cores.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
                          & Intel Core2 Duo (P8600)    & Intel Core2 Duo (P8600)     & Intel Xeon (L5640)\\
                          & (1 core, $2.40\unit{GHz}$) & (2 cores, $2.40\unit{GHz}$) & (6 cores, $2.27\unit{GHz}$)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$  & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators for
    for random parameter points.  The upper }
  \label{tab:run-time-comparison}
\end{table}

@@

\section{Speed test SLHA input file}
\label{sec:speed-test-slha-template-file}
%
\begin{verbatim}
Block MODSEL                 # Select model
    6    0                   # flavour violation
    1    1                   # mSUGRA
Block SMINPUTS               # Standard Model inputs
    1   1.279180000e+02      # alpha^(-1) SM MSbar(MZ)
    2   1.166390000e-05      # G_Fermi
    3   1.189000000e-01      # alpha_s(MZ) SM MSbar
    4   9.118760000e+01      # MZ(pole)
    5   4.200000000e+00      # mb(mb) SM MSbar
    6   1.709000000e+02      # mtop(pole)
    7   1.777000000e+00      # mtau(pole)
Block SOFTSUSY               # SOFTSUSY specific inputs
    1   1.000000000e-04      # tolerance
    2   2                    # up-quark mixing (=1) or down (=2)
    3   0                    # printout
    5   1                    # 2-loop running
    7   2                    # EWSB and Higgs mass loop order
Block FlexibleSUSY
    0   1.000000000e-04      # precision goal
    1   0                    # max. iterations (0 = automatic)
    2   0                    # algorithm (0 = two_scale, 1 = lattice)
    3   0                    # calculate SM pole masses
    4   1                    # pole mass loop order
    5   1                    # EWSB loop order
Block SPhenoInput            # SPheno specific input
    1  -1                    # error level
    2   1                    # SPA conventions
    11  0                    # calculate branching ratios
    13  0                    # include 3-Body decays
    12  1.000E-04            # write only branching ratios larger than this value
    31  -1                   # fixed GUT scale (-1: dynamical GUT scale)
    32  0                    # Strict unification
    34  1.000E-04            # Precision of mass calculation
    35  40                   # Maximal number of iterations
    37  1                    # Set Yukawa scheme
    38  2                    # 1- or 2-Loop RGEs
    50  1                    # Majorana phases: use only positive masses
    51  0                    # Write Output in CKM basis
    52  0                    # Write spectrum in case of tachyonic states
    55  1                    # Calculate one loop masses
    57  0                    # Calculate low energy constraints
    60  0                    # Include possible, kinetic mixing
    65  1                    # Solution tadpole equation
    75  0                    # Write WHIZARD files
    76  0                    # Write HiggsBounds file
    86  0.                   # Maximal width to be counted as invisible in Higgs decays
    510 0.                   # Write tree level values for tadpole solutions
    515 0                    # Write parameter values at GUT scale
    520 0.                   # Write effective Higgs couplings (HiggsBounds blocks)
    525 0.                   # Write loop contributions to diphoton decay of Higgs
Block MINPAR
    1   [50..1000]           # m0(MX)
    2   [50..1000]           # m12(MX)
    3   [1..100]             # tan(beta)(MZ) DRbar
    4   {-1,+1}              # sign(mu)
    5   [-1000..1000]        # A0(MX)
\end{verbatim}
